\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-22 paper/manuscript_paNote.tex
adding example and table

 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}. Official city websites allow mayors to present their views and policy priorities to the public. In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}. Local government websites are frequently visited by the public \citep{thomas2003new}. City websites can be used to communicate the stance of a mayor on social or economic programs.

%\begin{figure}
%\centering
%\includegraphics[scale=0.35]{figures/eriemayor}
%\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
%\label{fig:eriemayor}
%\end{figure}

@@

\subsubsection{Extracting Text from HTML}
The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate. In theory, HTML tags intended to mark text content  exist to prevent this problem. In practice, not every web developer adheres to this standard, and even when they do, there is a large degree of variation in the way it is implemented. Parsing any one website is fairly straightforward, but parsing the 283 different websites in our sample in a consistent and comparable manner makes a rule-based approach impossible.

We leverage methods developed in the information retrieval literature to deal with this problem. These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful. We rely on the method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited and can easily be implemented through the R package \texttt{boilerpipeR}.

@@

After all the preprocessing is set and done, our corpus consists of 259,099 documents.

@@

\input{tables/stmTopWords120_1.tex}
\input{tables/stmTopWords120_2.tex}

>>>>

 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}. Official city websites allow mayors to present their views and policy priorities to the public. In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}. Local government websites are frequently visited by the public \citep{thomas2003new}. City websites can be used to communicate the stance of a mayor on social or economic programs. Consider the example of the Gary, Indiana homepage, depicted in Figure \ref{fig:garymayor}.  This screenshot provides a clear example of the utility of a city website for communicating the mayor's policy priorities and accomplishments.

\begin{figure}
\centering
\includegraphics[scale=0.45]{figures/gary_hp}
\caption{Screenshot from the homepage at \url{https://garyin.us/}, accessed on 05/22/2019. Image depicts Democratic mayor of Gary, IN, Karen Freeman-Wilson.}
\label{fig:garymayor}
\end{figure}

@@

\subsubsection{Extracting Text from HTML}
The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate. In theory, HTML tags intended to mark text content  exist to prevent this problem. In practice, not every web developer adheres to this standard, and even when they do, there is a large degree of variation in the way it is implemented. Parsing any one website is fairly straightforward, but parsing the 283 different websites in our sample in a consistent and comparable manner makes a rule-based approach impossible. The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites. The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{garymayor}. Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site. The Mayor's message represents a relatively small fraction of the total text on the page.

\begin{figure}
\centering
\includegraphics[scale=0.35]{figures/gary_sidebyside}
\caption{Side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.}
\label{fig:garysbs}
\end{figure}

We leverage methods developed in the information retrieval literature to deal with this problem. These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful. We rely on the `boilerpipe' method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited, and can easily be implemented through the R package \texttt{boilerpipeR}. The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}. We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.

\begin{figure}
\centering
\includegraphics[scale=0.375]{figures/gary_bp}
\caption{Result of running \url{https://garyin.us/}, accessed on 05/22/2019, through the default boilerpipe algorithm at \url{https://boilerpipe-web.appspot.com/}.}
\label{fig:gary_bp}
\end{figure}

@@

After all the preprocessing is set and done, our corpus consists of 259,099 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package.

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software & gov2text \\
        \hline
        1. Assemble url list. & N/A & no \\
        2. Collect website files. & wget \& Selenium & no \\
        3.  & & \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline.} 
\end{table}

@@

\input{tables/stmTopWords120_1.tex}
\input{tables/stmTopWords120_2.tex}
\input{tables/stmTopWords120_1_OLD.tex}
\input{tables/stmTopWords120_2_OLD.tex}
